Poster_Plots

### 2022-11-13 Poster_plots.Rmd
upgraded plots with new widths and heights for poster

ggarrange(p1,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggsave(filename = "Poster_SMSE_LR_TV_Exp_mMSE.eps",device="eps",dpi=300,width = 12,height = 14)

ggarrange(p3,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggsave(filename = "Poster_MI_LR_TV_Exp_mMSE.eps",device="eps",dpi=300,width = 12,height = 14)

ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggsave(filename = "Poster_ACCURACY_LR_TV_Exp_mMSE.eps",device="eps",dpi=300,width = 12,height = 14)
```

>>>>

ggarrange(p3,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggsave(filename = "Poster_SMSE_LR_TV_Exp_mMSE.eps",device="eps",dpi=300,width = 14,height = 10)
